\begin{abstract}
\textcolor{red}{ISSUES: 2.1 - provide details of BERT vs. TF-IDF }
\noindent{\bf Context:}~\edit{\textmd{The correct prediction of long-lived bugs could help maintenance teams to build their plan and to fix more bugs that often adversely affect software quality and disturb the user experience across versions in FLOSS. Machine Learning (ML) and Text Mining methods have been applied to solve many real-world prediction problems, including those related to bug report handling.}}\\ 
\noindent{\bf Objective:}~\edit{\textmd{The purpose of our research is to compare the accuracy of ML classifiers on long-lived bug prediction in FLOSS using BERT- or TF-IDF-based feature extraction. Besides that, we aim to characterize bugs correctly predicted as long-lived and incorrectly predicted as short-lived.}}\\
\noindent{\bf Method:}~\textmd{We collected bug reports from six popular FLOSS and used the ML classifiers to predict long-lived bugs. Furthermore, we compare different feature extractors, based on BERT and TF-IDF methods, in long-lived bug prediction.}\\
\noindent{\bf Results:}~\edit{\textmd{We found that long-lived bug prediction using BERT-based feature extraction systematically outperformed the TF-IDF. The SVM and Random Forest outperformed others classifiers in almost all datasets using BERT. Furthermore, the accuracy of the best ML classifiers considering each feature extractor varied according to some attributes of bug reports.}}\\
\noindent{\bf Conclusion:}~\edit{\textmd{Our results demonstrated a promising avenue to predict long-lived bugs based on BERT contextual embeddings features.}}
\end{abstract}